On the Synchronization Power of the OpenFlow Data Plane

### 2015-05-22 inband-sync.tex
flow monitor

In order to read the current configuration of a switch (the existing flow entries), the controller should send
the OpenFlow \emph{add flow monitor} command with the \textsf{ofpt\_initial} optional flag.
In this paper, we indicate sending this message and gathering the
responds (the reply messages containing the flow entries) 
by \textit{read-config} statement which returns the configuration.

>>>>

To read the current configuration of a switch (the existing flow entries), the controller should send
the OpenFlow \emph{add flow monitor} command with the \textsf{ofpt\_initial} optional flag.
In this paper, we write \textit{read-config} for sending 
this message, receiving a response, and returning the received configuration.
